%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Long Sectioned Curriculum Vitae
% LaTeX Template
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{res} % Use the res.cls style

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one aboveHolly
\usepackage{etaremune}
\usepackage{xkeyval}

\newsectionwidth{0pt} % Stops section indenting

\newenvironment{packed_item}{
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}}
\newenvironment{packed_enum}{
\begin{enumerate}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{enumerate}}

\newcommand\lbi{\begin{packed_item}}
\newcommand\lei{\end{packed_item}}
\newcommand\lbn{\begin{packed_enum}}
\newcommand\len{\end{packed_enum}}

\begin{document}

	
%----------------------------------------------------------------------------------------
%	YOUR NAME AND ADDRESS(ES) SECTION
%----------------------------------------------------------------------------------------

\name{Peter M. Kekenes-Huskey, Ph.D.\\ \\} % Your name at the top

% If you don't want one of the addresses, simply remove all the text in the first or second \address{} bracket
\newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}}
\address{{\bf School Address} \\ Department of Chemistry \\ University of Kentucky\\ 219 Chemistry-Physics Building \\Lexington, KY 40506 \\ 
http://pkh.as.uky.edu} % Your address 1

\address{{\bf Permanent Address} \\ 307 Curtin Drive \\ Lexington, KY 40503 \\ pkekeneshuskey@uky.edu \\ (626) 644-9966} % Your address 2

%----------------------------------------------------------------------------------------

\begin{resume}

%%----------------------------------------------------------------------------------------
%%	OBJECTIVE SECTION
%%----------------------------------------------------------------------------------------
%
%\section{\centerline{OBJECTIVE}}
%
%\vspace{8pt} % Gap between title and text
%
%A position in Personnel Administration utilizing skills in recruiting, training and compensation.\\ 

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{EDUCATION}} 

\vspace{8pt} % Gap between title and text

{\sl Doctorate of Philosophy}, 
Chemistry  \\ 
California Institute of Technology, Pasadena, CA \hfill  Spring 2009 \\ 
%(GPA: 4.0 in major, 3.40 overall)
 
{\sl Bachelor of Science}, Chemistry \\ 
University of North Carolina, Asheville, NC \hfill May 2001 \\
\emph{Summa Cum Laude} %(GPA: 4.0)

%----------------------------------------------------------------------------------------
 
\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{PROFESSIONAL EXPERIENCE}} 

\vspace{8pt} % Gap between title and text

{\sl University of Kentucky, Lexington, KY } \hfill 2014 - present\\ 
Assistant Professor of Chemistry
%\lbi
%\item Multiscale modeling of cardiac function and diffusional processes
%\lei


{\sl University of California San Diego,  San
Diego CA [JA
McCammon, AD McCulloch] } \hfill 2010 - 2014\\ 
Postdoctoral scholar
%\lbi
%\item Multiscale modeling of cardiac function and diffusional processes
%\lei

{\sl Arete Associates, Staff Scientist, Northridge CA} \hfill 	2007 - 2010\\
Staff Scientist
%\lbi
%\item Signal processing, detection theory, algorithm design 
%\lei

{\sl Sandia National Laboratory, Albuquerque, NM.  [PS Crozier]} \hfill 	summer 2005\\
Summer Internship
%\lbi
%\item Free energy calculations for ion diffusion in silica nanopores
%\lei

{\sl California Institute of Technology, Pasadena, CA.  [WA Goddard, III]	 } \hfill 2001 - 2007\\
Graduate Student
%\lbi
%\item Drug design algorithm development and application
%\lei

{\sl Freie Universitaet zu Berlin, Berlin, Germany.  [EW Knapp]} \hfill 2001 - 2002\\
Fulbright fellow
%\lbi
%\item Molecular dynamics simulation of estrogen derivative binding to the estrogen receptor
%\lei

{\sl U. North Carolina, Asheville, NC.  [G Heard, BE Holmes]	} \hfill 1999 - 2001\\
Undergraduate researcher
%\lbi
%\item Quantum chemistry calculations of chlorofluorocarbon decomposition kinetics
%\lei

{\sl University of Cincinnati, OH.  [T Beck, W Connick]} \hfill 	summer 2000 \\
Summer researcher 
%\lbi
%\item Quantum chemistry calculations of electron transfer processes
%\lei


%{\sl International Business Machines} \hfill January -- August 1990 \\
%General Products Division, Tucson, AZ \hfill (Co-op Assignment)
%\begin{itemize} \itemsep -2pt % Reduce space between items
%\item Developed new selection criteria for applicant screening and selection at GPD Tucson. Conducted job analysis, wrote criteria, identified skill codes for applicant tracking, established rater reliability. 
%\item Interviewed applicants for positions in Assembly, Warehousing, and Direct Customer Response. 
%\item Assistant Co-op Coordinator. Initiated and maintained computer tracking for Co-op program. Organized all co-op seminars and activities, co-op directory. 
%\item Representative on GPD Compensation Task Force. Prepared job descriptions, assigned corporate position code, and submitted for division approval. 
%\end{itemize}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------
\newpage
\section{\centerline{RESEARCH EMPHASIS}}

\vspace{8pt} % Gap between title and text

{\sl Computational chemistry and biophysics}
\begin{itemize} \itemsep -2pt
\item Development and application of atomistic- to cellular-scale biological simulations
\item Molecular dynamics, finite element modeling 
\item Image processing, detection of weak signals in clutter and noise.  
\end{itemize}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{AWARDS}} 

\vspace{8pt} % Gap between title and text

%{\sl International Business Machines} \hfill January -- August 1990 \\
%General Products Division, Tucson, AZ \hfill (Co-op Assignment)
%\item 



{\sl Post-graduate}
\begin{itemize} \itemsep -12pt % Reduce space between items
\item National Institutes of Health Ruth Kirschstein Postdoctoral Fellow  \hfill 2013 \\
\item American Heart Association Western States Affiliates Postdoctoral
Fellow \hfill 2013 \\
\item Vice President Discretionary Award (Arete Associates)	\hfill 2010 \\
\end{itemize}

{\sl Graduate }
\begin{itemize} \itemsep -12pt % Reduce space between items
\item DOE Computational Science Graduate Fellow	\hfill 2004-2006  \\
\item National Science Foundation Fellow (declined for CSGF, 2003)	\hfill 2002-2003 \\
\item Department of Defense Fellowship (declined for NSF)  \hfill 2001 \\
\item Fulbright Fellow	\hfill 2001 \\
\end{itemize}

{\sl Undergraduate}
\begin{itemize} \itemsep -12pt % Reduce space between items
\item Manly Wright Award, Valedictorian of Graduating Class	\hfill 2001 \\
\item Outstanding Senior of the Western Carolinas American Chemical Society	\hfill 2001 \\
\item USA Today All-Academic 3rd Team	\hfill 2001 \\
\item Barry Goldwater Scholar in Science and Mathematics	\hfill 2000-2001 \\
\item W. Carolina ACS Schweizerhalle Scholarship	\hfill 2000-2001 \\
\item Phi Eta Sigma National Honors Fraternity	\hfill 1998 \\
\item Albina Mills Academic Scholarship	\hfill 1998-2001 \\
\item 4th Place UNCA Olivia-Jones Freshman Creative Writing Contest	\hfill 1999 \\
\end{itemize}

{\sl High School}
\begin{itemize} \itemsep -12pt % Reduce space between items
\item Eagle Scout	\hfill 1998 \\
\item Lion's Eye Bank Scholarship for Post-Secondary Education	\hfill 1998 \\
\item Presidential Scholar	\hfill 1998 \\
\item National Honors Society	\hfill 1997 \\
\end{itemize}

%----------------------------------------------------------------------------------------
%	PRESENTATIONS       
%----------------------------------------------------------------------------------------

\section{\centerline{INVITED TALKS}} 

\vspace{15pt} % Gap between title and text
% perl -ane 'chomp$_; $_=~s/\((\d+)\),\s*//; push(@a,$_." \\hfill $1 \\\\\n") if $_=~/\w+/; print reverse @a if $_=~/Simula Summer/' xxx

TBD, Simula Summer School, Norway, Oslo  \hfill 2015 \\

Quantifying the influence of the crowded cytoplasm on small molecule diffusion via homogenization theory, Bluegrass Molecular Biophysics Symposium, Lexington, KY  \hfill 2015 \\

Modeling of calcium signaling in cardiomyocytes, SIAM, Salt Lake City, UT \hfill 2015 \\

"Understanding intracellular signaling through computation", University of Kentucky Dept. of Chemical Engineering, Lexington, KY \hfill 2014 \\

"Multi-scale computational modeling of calcium signaling", Furman University, Greenville, SC  \hfill 2014 \\

"Understanding the chemistry of calcium signaling through computation", Oak Ridge National Labs, Oak Ridge, TN \hfill 2014 \\

"Multi-scale computational modeling of calcium signaling", Invited Poster at SciMix SERMACs meeting, Nashville, TN \hfill 2014 \\

"Electrostatic channeling of dihydrofolate in the dihydrofolate reductase/thymidylate synthase complex", American Chemical Society National Meeting, Dallas, CA \hfill 2014 \\

"Signaling in the Cardiomyocyte: A Molecular-to-Cellular-Scale Simulation Perspective", University of Arizona, Tucson, AZ \hfill 2014 \\

"Signaling in the cardiomyocyte: A molecular- to cellular-scale simulation perspective", Loyola University Health Sciences Campus, Chicago, IL \hfill 2014 \\

"Molecular signaling from ions to cardiac cells: a computational perspective", Northeastern University, Boston, MA \hfill 2013 \\

"Open problems in integrative studies of movement in living systems: Molecular to cellular scale modeling of myofibril function", University of Washington, Seattle, WA \hfill 2013 \\

"Continuum diffusion: a language for bridging  molecular and cellular scale signaling", University of North Carolina, Asheville, NC \hfill 2013 \\

"Homogenization of the Smoluchowski electro-diffusion equation for estimating hindered, anisotropic calcium diffusion in charged environments", Fall National ACS meeting, Indianapolis, IN \hfill 2013 \\

"Continuum diffusion: a language for bridging  molecular and cellular scale signaling", Simula Research Laboratory, Norway, Oslo \hfill 2013 \\

"Modeling of calcium diffusion at molecular and cellular scales: an application to the cardiomyocyte", CVRTI, University of Utah, Salt Lake City, UT \hfill 2013 \\

"Continuum diffusion: a language for bridging  molecular and cellular scale signaling", Department of Chemistry, University of Utah, Salt Lake City, UT \hfill 2013 \\

"Modeling of Ca2+ signaling in Cardiac Function", Gordon Research Seminar on Calcium Signaling, Waterville, ME \hfill 2011 \\

"Multi-scale Continuum Modeling and Simulation of Cardiac Function", Mathematics and Biochemistry-Biophysics Seminar at UCSD, San Diego, CA \hfill 2011 \\


%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	WORKSHOPS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{TEACHING EXPERIENCE}} 

\vspace{15pt} % Gap between title and text
CHE 105: Gen College Chemistry I, Lecturer, UK, Lexington, KY \hfill 2015 \\

"Mathematics of Physical Chemistry Boot Camp", Co-lecturer, UK, Lexington KY \hfill 2015

CHE 441: Physical Chemistry Lab, Lecturer, UK, Lexington, KY \hfill 2015 \\

CHE 105: Gen College Chemistry I, Lecturer, UK, Lexington, KY \hfill 2014 \\

CHEM 280: Applied Bioinformatics, Guest Lecturer, UCSD, San Diego, CA \hfill 2013 \\

BENG/CHEM 276: Numerical Analysis for Multi-Scale Biology, Guest Lecturer, UCSD, San Diego, CA \hfill 2013 \\

Mesoscale Modeling Track, NBCR Summer Institute, UCSD, San Diego, CA \hfill 2012 \\

"Sub-cellular models of calcium diffusion", NBCR Summer Institute, UCSD, San Diego, CA \hfill 2011 \\

"Multi-scale Modeling of Cardiac Function", Workshop at International Conference on Biological Physics, San Diego, CA \hfill 2011 \\

"Continuum Diffusion in Molecular Systems, NBCR Summer Institute, UCSD, San Diego, CA \hfill 2011 \\

"Special Topics in Signal Processing", Co-lecturer at Arete Associates staff education workshop series, Northridge, CA \hfill 2008 \\






%{\sl All courses entailed classroom lecture and lab instruction}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------
\newpage
\section{\centerline{PUBLICATIONS}}

\vspace{15pt} % Gap between title and text
\newcommand{\pmkh}{{\bf P.M. Kekenes-Huskey}}
{\sl * signifies equal contribution}

% how to create
% cut and paste new entries as references from Papers
% replace [1] with \item
% replace Kekenes-Huskey etc with \pmkh
% add co-first with *

\begin{etaremune} \itemsep 2pt % Reduce space between items
%\item {\bf P.M.Kekenes-Huskey}, A Edwards, J Hake, A Michailova, AD McCulloch, and JA McCammon, "Effects of t-system microanatomy and membrane transporter arrangement on Ca2+ trigger flux in normal and remodeled rabbit myocytes", (in prep)

\item S. Atalay, C. E. Scott, and  \pmkh, “Quantifying the influence of the crowded cytoplasm on ionic diffusion,” (submitted).

\item C. E. Scott and \pmkh, "Molecular basis of calcium-induced structural changes of human S100A1." (in review)

\item \pmkh, C. Eun, and A. McCammon, "Enzyme localization, crowding, and buffers collectively modulate diffusion-influenced signal transduction: Insights from continuum diffusion modeling," Journal of Chemical Physics, pp. 1-12, Sep. 2015.
\item S. Lindert, Y. Cheng, \pmkh, M. Regnier, and J. A. McCammon, "Effects of HCM cTnI mutation R145G on troponin structure and modulation by PKA phosphorylation elucidated by molecular dynamics simulations.," Biophys J, vol. 108, no. 2, pp. 395-407, Jan. 2015.
\item N. Wang, S. Zhou, \pmkh, B. Li, and J. A. McCammon, "Poisson-Boltzmann vs. Size-modified Poisson-Boltzmann Electrostatics Applied to Lipid Bilayers," J Phys Chem B, p. 141126142529007, Nov. 2014.
\item V. T. Metzger, C. Eun, \pmkh, G. Huber, and J. A. McCammon, "Electrostatic Channeling in P. falciparum DHFR-TS: Brownian Dynamics and Smoluchowski Modeling," Biophys J, vol. 107, no. 10, pp. 2394-2402, Nov. 2014.
\item Y. Cheng, S. Lindert, \pmkh, V. S. Rao, R. J. Solaro, P. R. Rosevear, R. Amaro, A. D. Mcculloch, J. A. McCammon, and M. Regnier, "Computational Studies of the Effect of the S23D/S24D Troponin I Mutation on Cardiac Troponin Structural Dynamics," Biophys J, vol. 107, no. 7, pp. 1675-1685, Oct. 2014.
\item \pmkh, A. K. Gillette, and J. A. McCammon, "Predicting the influence of long-range molecular interactions on macroscopic-scale diffusion by homogenization of the Smoluchowski equation," The Journal of chemical physics, vol. 140, no. 17, p. 174106, May 2014.
\item J. Hake, \pmkh, and A. D. Mcculloch, "Computational modeling of subcellular transport and signaling," Current Opinion in Structural Biology, vol. 25, pp. 92-97, Apr. 2014.
\item C. Eun, \pmkh*, V. T. Metzger, and J. A. McCammon, "A model study of sequential enzyme reactions and electrostatic channeling.," Journal of Chemical Physics, vol. 140, no. 10, pp. 105101-105101, Mar. 2014.
\item \pmkh, T. Liao, A. K. Gillette, J. E. Hake, Y. Zhang, A. P. Michailova, A. D. Mcculloch, and J. A. McCammon, "Molecular and subcellular-scale modeling of nucleotide diffusion in the cardiac myofilament lattice.," Biophys J, vol. 105, no. 9, pp. 2130-2140, Nov. 2013.
\item T. Liao, Y. Zhang, \pmkh, Y. Cheng, A. Michailova, A. D. McCulloch, M. Holst, and J. Mccammon, "Multi-core CPU or GPU-accelerated Multiscale Modeling for Biomolecular Complexes," Molecular Based , pp. 164-179, Oct. 2013.
\item C. Eun, \pmkh, and J. A. McCammon, "Influence of neighboring reactive particles on diffusion-limited reactions.," Journal of Chemical Physics, vol. 139, no. 4, pp. 044117-044117, Jul. 2013.
\item P. Setny, R. Baron, \pmkh, J. A. McCammon, and J. Dzubiella, "Solvent fluctuations in hydrophobic cavity-ligand binding kinetics," Proc Natl Acad Sci USA, vol. 110, no. 4, pp. 1197-1202, Jan. 2013.
\item \pmkh, S. Lindert, and J. McCammon, "Molecular basis of calcium-sensitizing and desensitizing mutations of the human cardiac troponin C regulatory domain: a multi-scale simulation study.," PLOS Computational Biology, vol. 8, no. 11, pp. e1002777-e1002777, Nov. 2012.
\item \pmkh*, V. Metzger*, B. Grant, and J. McCammon, "Calcium binding and allosteric signaling mechanisms for the sarcoplasmic reticulum Ca(2+)  ATPase.," Protein Sci., vol. 21, no. 10, pp. 1429-1443, Oct. 2012.
\item J. Hake, A. G. Edwards, Z. Yu, \pmkh, A. P. Michailova, J. A. McCammon, M. J. Holst, M. Hoshijima, and A. D. Mcculloch, "Modelling cardiac calcium sparks in a three-dimensional reconstruction of a calcium release unit.," The Journal of Physiology, vol. 590, no. 18, pp. 4403-4422, Sep. 2012.
\item S. Lindert, \pmkh, G. Huber, L. Pierce, and J. McCammon, "Dynamics and calcium association to the N-terminal regulatory domain of human cardiac troponin C: a multiscale computational study.," J Phys Chem B, vol. 116, no. 29, pp. 8449-8459, Jul. 2012.
\item \pmkh, Y. Cheng, J. Hake, F. Sachse, J. Bridge, M. Holst, A. McCulloch, J. McCammon, and A. Michailova, "Modeling effects of L-type ca(2+) current and na(+)-ca(2+) exchanger on ca(2+) trigger flux in rabbit myocytes with realistic T-tubule geometries.," Front Physiol, vol. 3, pp. 351-351, Jan. 2012.
\item Y. Cheng, \pmkh, J. E. Hake, M. J. Holst, J. A. McCammon, and A. P. Michailova, "Multi-scale continuum modeling of biological processes: from molecular electro-diffusion to sub-cellular signaling transduction," Comput Sci Discov, vol. 5, no. 1, p. 015002, 2012.
\item \pmkh, A. Gillette, J. Hake, and J. A. McCammon, "Finite-element estimation of protein-ligand association rates with post-encounter effects: applications to calcium binding in troponin C and SERCA," Comput Sci Discov, vol. 5, no. 1, p. 014015, 2012.
\item S. Lindert, \pmkh, and J. A. McCammon, "Long-Timescale Molecular Dynamics Simulations Elucidate the Dynamics and Kinetics of Exposure of the Hydrophobic Patch in Troponin C," Biophys J, vol. 103, no. 8, pp. 1784-1789, 2012.
\item \pmkh, Y. Cheng, and J. Hake, "Contributions of Structural t-Tubule Heterogeneities and Membrane Ca2+ Flux Localization to Local Ca2+ Signaling in Rabbit Ventricular Myocytes," Biophysical , 2011.
\item \pmkh, A Monte Carlo-based torsion construction algorithm for ligand design. Doctoral Thesis, 2009.
\item J. Heo, S. Han, N. Vaidehi, J. Wendel, \pmkh, and W. Goddard III, "Prediction of the 3D Structure of FMRF?amide Neuropeptides Bound to the Mouse MrgC11 GPCR and Experimental Validation," ChemBioChem, vol. 8, no. 13, pp. 1527-1539, 2007.
\item J. D. Ferguson, N. L. Johnson, \pmkh, W. C. Everett, G. L. Heard, D. W. Setser, and B. E. Holmes, "Unimolecular Rate Constants for HX or DX Elimination (X = F, Cl) from Chemically Activated CF 3CH 2CH 2Cl, C 2H 5CH 2Cl, and C 2D 5CH 2Cl:  Threshold Energies for HF and HCl Elimination," J. Phys. Chem. A, vol. 109, no. 20, pp. 4540-4551, May 2005.
\item A. E. Cho, J. A. Wendel, N. Vaidehi, \pmkh, W. B. Floriano, P. K. Maiti, and W. A. Goddard, "The MPSim-Dock hierarchical docking algorithm: Application to the eight trypsin inhibitor cocrystals," J Comput Chem, vol. 26, no. 1, pp. 48-71, 2004.
\item \pmkh, I. Muegge, and M. Rauch, "A molecular docking study of estrogenically active compounds with 1, 2-diarylethane and 1, 2-diarylethene pharmacophores," Bioorganic\& medicinal, 2004.
\item \pmkh, N. Vaidehi, W. B. Floriano, and W. Goddard III, "Fidelity of phenylalanyl-tRNA synthetase in binding the natural amino acids," J Phys Chem B, vol. 107, no. 41, pp. 11549-11557, 2003.

\end{etaremune}



%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	FUNDING SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{FUNDING}} 
\newcommand{\lead}{$^*$}
\newcommand{\contrib}{$\dag$}
{\sl \lead sole or lead investigator}
{\sl \contrib significant contributions} 
\vspace{0pt} % Reduce space between section title and contents

University of Kentucky, Igniting Research Collaborations Award \lead \hfill 05/15-08/15 \\
"Simulations of dysregulated intracellular Ca2+-handling in diabetic cardiomyopathy"  \\
PKH: \$25,495 / Total: \$25,495.

XSEDE, Supercomputer award, \lead \hfill 2014\\
"SERCA and its role in cardiac signaling" \\
PKH: \$148,433 equiv.  

NIGMS, Competitive Renewal (3 P41GM103426-20)\contrib\hfill 2014 \\
Total: \$1,990,191 

NHLBI, National Research Service Award\lead  \hfill 2013 \\  % priority score 22
PKH: \$84,000/ Total \$84,000

American Heart Association, Western Affiliates Postdoctoral Fellowship\lead \hfill 2013 \\
PKH: \$88,000 / Total: \$88,000 

Anton supercomputer award, \contrib \hfill 2014\\
"Simulations to characterize skeletal muscle Ca2+-binding proteins" 

NIGMS,  Supplementary Award  (3 P41 GM103426-19S1)\contrib  \hfill 2012 \\
Total: \$367,613 

Anton supercomputer award, \contrib \hfill 2013 \\
"Microsecond scale simulations to characterize ... full length troponin"

XSEDE, Supercomputer award \contrib \hfill 2012 

Anton supercomputer award,  \hfill 2011 \\
"Using microsecond scale dynamics to characterize different classes of allosteric interactions" 

Anton supercomputer award,  \contrib \hfill 2011 \\
"Using microsecond scale dynamics ...  allosteric interactions"

XSEDE,  Startup award for examination of conformational dynamics in SERCA\lead \hfill 2011 

% https://www.sbir.gov/sbirsearch/detail/2029
\noindent DoD/Navy, Phase I SBIR \contrib \hfill 2010 \\
"Image Fusion for Submarine Imaging Systems"\\
Total:\$99991 

%Phase I SBIR Automatic Target Recognition (ATR) Algorithm for Submarine Periscope Systems\contrib (DoD \$100,000) \hfill 2008 \\
% I'm not sure if I helped w writing this Phase I SBIR ... Algorithm for Submarine Periscope Systems\contrib (DoD \$100,000) \hfill 2008 \\
% http://www.sbir.gov/sbirsearch/detail/2037
DoD, Phase I SBIR \contrib  \hfill 2010 \\
"Investigation of the Debye Effect for Submarine Detection" \\
Total: \$79,995 

% http://www.sbir.gov/sbirsearch/detail/96879
%Phase II SBIR Automatic Target Recognition (ATR) Algorithm for Submarine Periscope Systems\contrib (DoD, \$1,267,015)  \hfill  2009 \\
DoD, Phase II SBIR\contrib \hfill 2009 \\
Algorithm for Submarine Periscope Systems \\ 
Total: \$1,267,015 

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	SOFTWARE SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{SOFTWARE}}
\vspace{0pt} 
\noindent 
\textsc{smolfin} Diffusion-limited association reactions
\textsc{EnzymeKineticsACS} Spatially-decoupled biochemical reactions
\textsc{Smolhomog} Homogenized Smoluchowski solver
\textsc{homogenization} Multi-scale estimates of diffusion tensors
\textsc{sarcomere} Metabolism in half-sarcomere 

%----------------------------------------------------------------------------------------
%	SERVICE SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{SERVICE}} 

\vspace{0pt} % Reduce space between section title and contents
{\sl University of Kentucky} \\
Naff Symposium Organizer \hfill 2015\\
Graduate Recruiting Committee \hfill 2014-present\\
Website Committee \hfill 2014-present \\
Research/Scholarship Advisory Committee \hfill 2014-present\\
Faculty Advisor to Society of Postdocs \hfill 2014-present\\

{\sl External } \\    
Handling editor for Frontiers Special Topic Issue \hfill 2015 \\
Petroleum Research Fund proposal review \hfill 2015 \\
XRAC Review Committee \hfill 2015-present\\
Manuscript reviewed for Biophysical Journal  \hfill 2015 \\
Manuscripts reviewed for FEBS Letters, Biophysical Journal  \hfill 2014 \\
Manuscript reviewed for PNAS \hfill 2013 \\
Computation Science Graduate Fellowship screening committee \hfill 2012-present \\
Coordinator of Caltech Alumni Association events in San Diego/Lexington \hfill 2012-present \\
Mini-symposium co-organizer at SIAM Life Sciences meeting, San Diego, CA \hfill 2012 \\
Chaired session at Domain Decomposition Meeting, San Diego, CA \hfill 2011 \\
JAM Steering committee \hfill 2011-2014 \\

\section{\centerline{TRAINING}} 
Cottrell Scholars New Faculty Workshop, Washington DC \hfill 2015\\
Center for the Physics of Living Cells Summer School (UIUC) \hfill 2013\\ 
Scientific Ethics (UCSD) \hfill 2013\\ 
College Classroom (Center for Teaching Development, UCSD) \hfill 2013\\
San Diego Lab Management Symposium participant \hfill 2010 \\

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections


%----------------------------------------------------------------------------------------
%	MEMBERSHIPS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{MEMBERSHIPS}} 

\vspace{-5pt} % Reduce space between section title and contents

\begin{center}
American Chemical Society\\
Biophysical Society \\
American Heart Association \\
\end{center}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections


%----------------------------------------------------------------------------------------
%	MISC TALKS
%----------------------------------------------------------------------------------------

\section{\centerline{PRESENTATIONS}} 

\vspace{15pt} % Gap between title and text
Muscle Forum, University of Kentucky   \hfill 2015 \\

Society of Post-docs, University of Kentucky \hfill 2015 \\

Heart Working Group, University of Kentucky \hfill 2014 \\

Students of the American Chemical Society, University of Kentucky \hfill 2014 \\

"Multi-scale simulations of diffusion-influenced reactions", Poster at Gordon Research Conference, Mount Snow Resort, NH \hfill 2014 \\

"Multi-scale simulations of diffusion-influenced reactions", Talk at William Goddard, III's Birthday Symposium, Pasadena, CA \hfill 2014 \\

"Multi-scale simulations of diffusion-influenced reactions", Poster at ACS National Meeting, Dallas, TX \hfill 2014 \\

"Multi-scale Continuum Modeling and Simulation of Cardiac Function, Talk at Nifty Fifty, Kearny High School, San Diego, CA \hfill 2014 \\

"A Markov-state model for the regulation of the sarcoplasmic reticulum Ca2+ ATPase by phospholamban",  Poster at Biophysical Society Meeting, San Francisco, CA \hfill 2014 \\

"Continuum diffusion: a language for bridging  molecular and cellular scale signaling", Talk at Georgia State University, Atlanta, GA \hfill 2013 \\

"Building a molecular to cellular-scale understanding of Troponin function through simulation", Talk at Ohio State University, Columbus, OH \hfill 2013 \\

"Continuum diffusion: a language for bridging  molecular and cellular scale signaling", Talk at Carnegie Mellon, Pittsburgh, PA \hfill 2013 \\

"Modeling Calcium Dynamics in Realistic Rabbit Ventricular Myocytes with Several Transverse Tubules", Poster at Alternative Muscle Club Meeting, University of California, San Diego  \hfill 2013 \\

"Multi-scale Continuum Modeling and Simulation of Cardiac Function, Talk at Nifty Fifty, Sweetwater High School, El Cajon, CA \hfill 2013 \\

"Substrate association as a two stage process: the diffusional encounter and post-encounter binding", Talk at Modeling Diffusional Encounter and Subsequent Events Mini-Symposium, San Diego, CA  \hfill 2012 \\

"Multi t-tubule modeling: M-times better than a single t-tubule", Talk at Cardiac Physiome Brainstorming session, San Diego, CA  \hfill 2012 \\

"Molecular and sub-cellular modeling of cardiac Troponin C calcium handling", Talk at SIAM Life Sciences Meeting, San Diego, CA  \hfill 2012 \\

"Molecular electrostatics and Diffusion", Talk at NBCR Summer Institute, San Diego, CA \hfill 2012 \\

"High-level science: a dogma for research and employment?", Talk at CSGF Alumni Meeting, Washington DC  \hfill 2012 \\

"Modeling Calcium Dynamics in Realistic Rabbit Ventricular Myocytes with Several Transverse Tubules", Poster at Gordon Conference on Muscle Excitation Contraction, Les Diableret, Switzerland  \hfill 2012 \\

"Stochastic gating regulates calcium association rates in Troponin C and SERCA", Talk at American Chemical Society Meeting, San Diego, CA \hfill 2012 \\

"Molecular and sub-cellular modeling of Ca2+ signaling in cardiomyocytes", Talk for Nifty Fifty, San Diego High School, San Diego, CA  \hfill 2012 \\

"Modeling Calcium Dynamics in Realistic Rabbit Ventricular Myocytes with Several Transverse Tubules", Poster at Biophysical Society Meeting, San Diego, CA  \hfill 2012 \\

"Contributions of structural t-tubule heterogeneities in local Ca2+ signaling in rabbit ventricular myocytes", Poster at NBCR Summer Institute, UCSD, San Diego, CA (Awarded Best Poster) \hfill 2011 \\

"Contributions of structural t-tubule heterogeneities in local Ca2+ signaling  in rabbit ventricular myocytes", Poster at Cardiac Physiome Workshop, Oxford, England \hfill 2011 \\

"Contributions of structural t-tubule heterogeneities in local Ca2+ signaling in rabbit ventricular myocytes", Poster at Gordon Conference on Calcium Signaling, Waterville, ME \hfill 2011 \\

"Accelerated molecular dynamics of sarcoplasmic reticulum  Ca2+ ATPase (SERCA) structural transitions", Poster at International Conference on Biological Physics, San Diego, CA \hfill 2011 \\

"Sub-cellular Ca2+ signaling in cardiac myocytes", Talk at NBCR RAC meeting, UCSD, San Diego, CA \hfill 2011 \\

"Contributions of structural t-tubule heterogeneities and membrane Ca2+ flux localization to local Ca2+ signaling in rabbit ventricular myocytes", Poster at Biophysical Society Meeting, Baltimore, MD  \hfill 2011 \\

"Multi-scale Continuum Modeling and Simulation of Cardiac Function", Talk at Nifty Fifty High School Outreach, Carlsbad, CA \hfill 2011 \\

"Effects of membrane calcium flux localizations and realistic t-tubule geometry on cardiac excitation contraction coupling", Mini-talk at Biological Diffusion and Brownian Dynamics Brainstorm 2 at UCSD, San Diego, CA \hfill 2010 \\


\end{resume} 
\end{document}
