

\name{Peter M. Kekenes-Huskey, Ph.D.\\ \\} % Your name at the top

% If you don't want one of the addresses, simply remove all the text in the first or second \address{} bracket
\newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}}
\address{{\bf School Address} \\ Department of Chemistry \\ University of Kentucky\\ 219 Chemistry-Physics Building \\Lexington, KY 40506 \\ 
http://pkh.as.uky.edu} % Your address 1

\address{{\bf Permanent Address} \\ 307 Curtin Drive \\ Lexington, KY 40503 \\ pkekeneshuskey@uky.edu \\ (626) 644-9966} % Your address 2

%----------------------------------------------------------------------------------------
\begin{resume}

%%----------------------------------------------------------------------------------------
%%	OBJECTIVE SECTION
%%----------------------------------------------------------------------------------------
%
%\section{\centerline{OBJECTIVE}}
%
%\vspace{8pt} % Gap between title and text
%
%A position in Personnel Administration utilizing skills in recruiting, training and compensation.\\ 

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{EDUCATION}} 
\vspace{8pt} % Gap between title and text
{\sl California Institute of Technology, Chemistry } \hfill  Ph.D., 2009 \\ 
{\sl University of North Carolina Asheville, Chemistry} \hfill B.S., 2001 \\

%----------------------------------------------------------------------------------------
 
\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{PROFESSIONAL EXPERIENCE}} 

\vspace{8pt} % Gap between title and text

{\sl Assistant Professor, Chemistry, University of Kentucky} \hfill 2014 - present\\ 
{\sl Postdoctoral fellow, University of California San Diego } \hfill 2010 - 2014\\ 
{\sl Staff Scientist, Arete Associates} \hfill 	2007 - 2010\\
{\sl Intern, Sandia National Laboratory} \hfill 	summer 2005\\
{\sl Graduate Fellow, California Institute of Technology} \hfill 2001 - 2007\\
{\sl Fulbright Fellow, Freie Universitaet zu Berlin} \hfill 2001 - 2002\\
{\sl Undergraduate Researcher, U. North Carolina, Asheville} \hfill 1999 - 2001\\
{\sl Summer researcher, University of Cincinnati} \hfill 	summer 2000 \\

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{Products}}
Five most relevant publications to this project (Total of 31)
\vspace{15pt} % Gap between title and text
\newcommand{\pmkh}{{\bf P.M. Kekenes-Huskey}}
{\sl * signifies equal contribution}

\begin{etaremune} \itemsep 2pt % Reduce space between items
%\item {\bf P.M.Kekenes-Huskey}, A Edwards, J Hake, A Michailova, AD McCulloch, and JA McCammon, "Effects of t-system microanatomy and membrane transporter arrangement on Ca2+ trigger flux in normal and remodeled rabbit myocytes", (in prep)

\item E. C. Cook, B. Sun, \pmkh\ and T.P. Creamer,"Electrostatic Forces Mediate Fast Association of Calmodulin and the Intrinsically Disordered Regulatory Domain of Calcineurin." 2016. \arxiv{1611.04080}
\item JK Siddiqui, SB Tikunova, SD Walton, M Meyer, PP de Tombe, N Neilson, \pmkh, HE Salhi, PML Janssen, BJ Biesiadecki, JP Davis, "Myofilament Calcium Sensitivity:  Consequences of the Effective Concentration of Troponin I," Frontiers in Physiology, 2016, 7:632. \pmid{28066265}
\item A.N. Kucharski, C.E. Scott, J.P. Davis and \pmkh, "Understanding Ion Binding Affinity and Selectivity in $\beta$ Parvalbumin Using Molecular Dynamics and Mean Sphere Approximation Theory," J Phys Chem B, 2016, 120(33):8617-30 \pmid{28066265}
\item \pmkh, C. E. Scott, and S. Atalay, "Quantifying the influence of the crowded cytoplasm on ionic diffusion," J Phys Chem B 2016, 120(33):8696-706 \pmid{27327486}
\item C. E. Scott and \pmkh, "Molecular basis of calcium-induced structural changes of human S100A1," Biophys J, Mar. 2016, 110(5):1052-1063 \pmid{26958883}

\end{etaremune}

\begin{comment}
\section{\centerline{Other Significant Products}}
Five other significant publications (Total of 30)

\begin{etaremune} \itemsep 2pt % Reduce space between items
\item \pmkh, A. K. Gillette, and J. A. McCammon, "Predicting the influence of long-range molecular interactions on macroscopic-scale diffusion by homogenization of the Smoluchowski equation," The Journal of chemical physics, vol. 140, no. 17, p. 174106, May 2014.
\item C. Eun, \pmkh*, V. T. Metzger, and J. A. McCammon, "A model study of sequential enzyme reactions and electrostatic channeling.," Journal of Chemical Physics, vol. 140, no. 10, pp. 105101-105101, Mar. 2014.
\item \pmkh, T. Liao, A. K. Gillette, J. E. Hake, Y. Zhang, A. P. Michailova, A. D. Mcculloch, and J. A. McCammon, "Molecular and subcellular-scale modeling of nucleotide diffusion in the cardiac myofilament lattice.," Biophys J, vol. 105, no. 9, pp. 2130-2140, Nov. 2013.
\item \pmkh, S. Lindert, and J. McCammon, "Molecular basis of calcium-sensitizing and desensitizing mutations of the human cardiac troponin C regulatory domain: a multi-scale simulation study.," PLOS Computational Biology, vol. 8, no. 11, pp. e1002777-e1002777, Nov. 2012.
\item \pmkh, A. Gillette, J. Hake, and J. A. McCammon, "Finite-element estimation of protein-ligand association rates with post-encounter effects: applications to calcium binding in troponin C and SERCA," Comput Sci Discov, vol. 5, no. 1, p. 014015, 2012.
\end{etaremune}
\end{comment}

%%% FUnding
\newpage
\input{components/funding}

\section{\centerline{SYNERGISTIC ACTIVITIES}} 
\vspace{8pt} % Gap between title and text

{\sl Courses Taught: General Chemistry, Physical Chemistry for Engineers, Physical Chemistry Lab} \hfill 2014 - present\\ 
{\sl Manuscripts reviewed (10+) for several journals} \hfill 2014 - present\\ 
{\sl Proposals reviewed for NSF, ACS} \hfill 2015 - present\\ 
{\sl Standing member of NSF XSEDE Review Panel} \hfill 2015 - present\\ 
{\sl Standing member of DOE CS Graduate Fellowship Review Committee} \hfill 2012 - present\\ 




\vspace{0.2in} % Some whitespace between sections
\end{resume} 
