%To gen. list 
%\documentclass{article}
%\begin{document}
%\autocite{KekenesHuskey:l_olPRe3,Setny:2013dw,Kekenes-Huskey2012c,Kekenes-Huskey2012b,Kekenes-Huskey2012a,Hake2012,Lindert2012a,Kekenes-Huskey2012,Cheng:vn,Lindert:IuL24PVU,Kekenes-Huskey2011,KekenesHuskey:2009wh,Heo:2007ty,Ferguson:2005cf,Vaidehi:2005ue,KekenesHuskey:2004va,KekenesHuskey:2003uf,Kekenes-Huskey2014a,Liao:ARrpx_SV,Hake:q7b0C29I,Eun2013}

%\bibliographystyle{jbact}
%\bibliography{/home/huskeypm/notes/pkh}
%\end{document}

% how to create
% ALL ENTRIES MUST BE ON SINGLE LINE FOR OzthER SCRIPTS TO WORK 
% cut and paste new entries as references from Papers
% replace [1] with \item
% replace Kekenes-Huskey etc with \pmkh
% add co-first with *
% Be sure to add PMID via \pmid{} command 
\newcommand\ug{$^+$}
\vspace{15pt} % Gap between title and text
\section{\centerline{PUBLICATIONS}}
\newcommand{\pmkh}{{\bf P.M. Kekenes-Huskey}}\vspace{10pt}

\centerline{\sl * equal contribution,  \ug\ undergraduate author}
\vspace{10pt}
\newcommand\total{33} % total - under review 
\centerline{ \uline{(8/\total\ as faculty member)}}
\begin{etaremune} \itemsep 2pt % Reduce space between items
\item Shen, X., Brink, J. van den, Hou, Y., Colli, D., Le, C., Kolstad, T. R., \pmkh, Louch, W. E. (2018). 3D dSTORM imaging reveals novel detail of ryanodine receptor localization in rat cardiac myocytes. The Journal of Physiology. (in print)
\item \textit{P. Wagh, X. Zhang, R. Blood\ug, \pmkh, P. Rajapaksha, Y. Wei and I. Escobar, 
"Alignment and Immobilization of Aquaporins on Polybenzimidazole Nanofiltration Membranes" (under review)}
\item \textit{Dylan Colli\ug\ et al, \pmkh,
"GPU accelerated detection and classication of myocyte transverse tubule ultra-structure",
(\href{https://www.biorxiv.org/content/early/2018/07/17/371328}{bioarxiv 371328}, under revison)}
\item Sun, B., Cook, E. C., Creamer, T. P., and \pmkh (2018). Electrostatic control of calcineurin’s intrinsically-disordered regulatory domain binding to calmodulin. Biochimica et Biophysica Acta (BBA) - General Subjects, 1862(12), 2651-2659. \pmid{30071273}
\item \textit{Byeongjae Chun, Bradley D Stewart, Darin D Vaughan\ug\, Adam S Bachstetter, \pmkh,
"Simulation of P2X-mediated calcium signaling in microglia" 
(\href{https://www.biorxiv.org/content/early/2018/06/24/354142}{354142}, under revision)}
\item Bin Sun, Ryan Blood\ug\, Selcuk Atalay, Dylan Colli\ug\, Stephen E. Rankin, Barbara L. Knutson and \pmkh, "Simulation-based characterization of electrolyte and small molecule diffusion in imaged oriented mesoporous silica thin films", 
(chemRxiv: \href{https://doi.org/10.26434/chemrxiv.5533066.v1}{5533066}) (in press)
\item Stewart, B. D., Scott, C. E., McCoy, T. P., Yin, G., Despa, F., Despa, S., and \pmkh. (2018). "Computational modeling of amylin-induced calcium dysregulation in rat ventricular cardiomyocytes." Cell Calcium, 71, 65-74. \pmid{29604965}
\item \textit{E. C. Cook, B. Sun, \pmkh\ and T.P. Creamer,"Electrostatic Forces Mediate Fast Association of Calmodulin and the Intrinsically Disordered Regulatory Domain of Calcineurin." 2016. \arxiv{1611.04080} (under revision)}
\item JK Siddiqui, SB Tikunova, SD Walton, M Meyer, PP de Tombe, N Neilson, \pmkh, HE Salhi, PML Janssen, BJ Biesiadecki, JP Davis, "Myofilament Calcium Sensitivity:  Consequences of the Effective Concentration of Troponin I," Frontiers in Physiology, 2016, 7:632. \pmid{28066265}
\item A.N. Kucharski$^+$, C.E. Scott, J.P. Davis and \pmkh, "Understanding Ion Binding Affinity and Selectivity in $\beta$ Parvalbumin Using Molecular Dynamics and Mean Sphere Approximation Theory," J Phys Chem B, 2016, 120(33):8617-30 \pmid{28066265}
\item \pmkh, C. E. Scott, and S. Atalay, "Quantifying the influence of the crowded cytoplasm on ionic diffusion," J Phys Chem B 2016, 120(33):8696-706 \pmid{27327486}
\item C. E. Scott and \pmkh, "Molecular basis of calcium-induced structural changes of human S100A1," Biophys J, Mar. 2016, 110(5):1052-1063 \pmid{26958883}
\item \pmkh, C. Eun, and A. McCammon, "Enzyme localization, crowding, and buffers collectively modulate diffusion-influenced signal transduction: Insights from continuum diffusion modeling," Journal of Chemical Physics, 2015, 143(9):1-12. \pmid{26342355}
\vspace{20pt}
\\
%\end{etaremune}
\centerline{ (25/\total\ up through postdoctoral studies)}
\vspace{-10pt}
%\begin{etaremune}
%\setcounter{enumi}{11} % value of last entry
\item S. Lindert, Y. Cheng, \pmkh, M. Regnier, and J. A. McCammon, "Effects of HCM cTnI mutation R145G on troponin structure and modulation by PKA phosphorylation elucidated by molecular dynamics simulations.," Biophys J, vol. 108, no. 2, pp. 395-407, Jan. 2015. \pmid{25606687}
\item N. Wang, S. Zhou, \pmkh, B. Li, and J. A. McCammon, "Poisson-Boltzmann vs. Size-modified Poisson-Boltzmann Electrostatics Applied to Lipid Bilayers," J Phys Chem B, p. 141126142529007, Nov. 2014. \pmid{25426875}
\item V. T. Metzger, C. Eun, \pmkh, G. Huber, and J. A. McCammon, "Electrostatic Channeling in P. falciparum DHFR-TS: Brownian Dynamics and Smoluchowski Modeling," Biophys J, vol. 107, no. 10, pp. 2394-2402, Nov. 2014. \pmid{25418308}
\item Y. Cheng, S. Lindert, \pmkh, V. S. Rao, R. J. Solaro, P. R. Rosevear, R. Amaro, A. D. Mcculloch, J. A. McCammon, and M. Regnier, "Computational Studies of the Effect of the S23D/S24D Troponin I Mutation on Cardiac Troponin Structural Dynamics," Biophys J, vol. 107, no. 7, pp. 1675-1685, Oct. 2014.\pmid{25296321}
\item \pmkh, A. K. Gillette, and J. A. McCammon, "Predicting the influence of long-range molecular interactions on macroscopic-scale diffusion by homogenization of the Smoluchowski equation," The Journal of chemical physics, vol. 140, no. 17, p. 174106, May 2014.\pmid{23293662}
\item J. Hake, \pmkh, and A. D. Mcculloch, "Computational modeling of subcellular transport and signaling," Current Opinion in Structural Biology, vol. 25, pp. 92-97, Apr. 2014.\pmid{24509246}
\item C. Eun, \pmkh*, V. T. Metzger, and J. A. McCammon, "A model study of sequential enzyme reactions and electrostatic channeling.," Journal of Chemical Physics, vol. 140, no. 10, pp. 105101-105101, Mar. 2014.\pmid{24628210}
\item \pmkh, T. Liao, A. K. Gillette, J. E. Hake, Y. Zhang, A. P. Michailova, A. D. Mcculloch, and J. A. McCammon, "Molecular and subcellular-scale modeling of nucleotide diffusion in the cardiac myofilament lattice.," Biophys J, vol. 105, no. 9, pp. 2130-2140, Nov. 2013.\pmid{24209858}
\item T. Liao, Y. Zhang, \pmkh, Y. Cheng, A. Michailova, A. D. McCulloch, M. Holst, and J. Mccammon, "Multi-core CPU or GPU-accelerated Multiscale Modeling for Biomolecular Complexes," Molecular Based , pp. 164-179, Oct. 2013.\pmid{24352481}
\item C. Eun, \pmkh, and J. A. McCammon, "Influence of neighboring reactive particles on diffusion-limited reactions.," Journal of Chemical Physics, vol. 139, no. 4, pp. 044117-044117, Jul. 2013.\pmid{23901970}
\item P. Setny, R. Baron, \pmkh, J. A. McCammon, and J. Dzubiella, "Solvent fluctuations in hydrophobic cavity-ligand binding kinetics," Proc Natl Acad Sci USA, vol. 110, no. 4, pp. 1197-1202, Jan. 2013.\pmid{23297241}
\item \pmkh, S. Lindert, and J. McCammon, "Molecular basis of calcium-sensitizing and desensitizing mutations of the human cardiac troponin C regulatory domain: a multi-scale simulation study.," PLOS Computational Biology, vol. 8, no. 11, pp. e1002777-e1002777, Nov. 2012.\pmid{23209387}
\item \pmkh*, V. Metzger*, B. Grant, and J. McCammon, "Calcium binding and allosteric signaling mechanisms for the sarcoplasmic reticulum Ca(2+)  ATPase.," Protein Sci., vol. 21, no. 10, pp. 1429-1443, Oct. 2012.\pmid{22821874}
\item J. Hake, A. G. Edwards, Z. Yu, \pmkh, A. P. Michailova, J. A. McCammon, M. J. Holst, M. Hoshijima, and A. D. Mcculloch, "Modelling cardiac calcium sparks in a three-dimensional reconstruction of a calcium release unit.," The Journal of Physiology, vol. 590, no. 18, pp. 4403-4422, Sep. 2012.\pmid{22495592}
\item S. Lindert, \pmkh, G. Huber, L. Pierce, and J. McCammon, "Dynamics and calcium association to the N-terminal regulatory domain of human cardiac troponin C: a multiscale computational study.," J Phys Chem B, vol. 116, no. 29, pp. 8449-8459, Jul. 2012.\pmid{22329450}
\item \pmkh, Y. Cheng, J. Hake, F. Sachse, J. Bridge, M. Holst, A. McCulloch, J. McCammon, and A. Michailova, "Modeling effects of L-type ca(2+) current and na(+)-ca(2+) exchanger on ca(2+) trigger flux in rabbit myocytes with realistic T-tubule geometries.," Front Physiol, vol. 3, pp. 351-351, Jan. 2012.\pmid{23060801}
\item Y. Cheng, \pmkh, J. E. Hake, M. J. Holst, J. A. McCammon, and A. P. Michailova, "Multi-scale continuum modeling of biological processes: from molecular electro-diffusion to sub-cellular signaling transduction," Comput Sci Discov, vol. 5, no. 1, p. 015002, 2012.\pmid{23505398}
\item \pmkh, A. Gillette, J. Hake, and J. A. McCammon, "Finite-element estimation of protein-ligand association rates with post-encounter effects: applications to calcium binding in troponin C and SERCA," Comput Sci Discov, vol. 5, no. 1, p. 014015, 2012.\pmid{23293662}
\item S. Lindert, \pmkh, and J. A. McCammon, "Long-Timescale Molecular Dynamics Simulations Elucidate the Dynamics and Kinetics of Exposure of the Hydrophobic Patch in Troponin C," Biophys J, vol. 103, no. 8, pp. 1784-1789, 2012. \pmid{23083722}
%\item \pmkh, Y. Cheng, and J. Hake, "Contributions of Structural t-Tubule Heterogeneities and Membrane Ca2+ Flux Localization to Local Ca2+ Signaling in Rabbit Ventricular Myocytes," Biophysical , 2011.
\item \pmkh, A Monte Carlo-based torsion construction algorithm for ligand design. Doctoral Thesis, 2009. 
\item J. Heo, S. Han, N. Vaidehi, J. Wendel, \pmkh, and W. Goddard III, "Prediction of the 3D Structure of FMRF?amide Neuropeptides Bound to the Mouse MrgC11 GPCR and Experimental Validation," ChemBioChem, vol. 8, no. 13, pp. 1527-1539, 2007.\pmid{17647204}
\item J. D. Ferguson, N. L. Johnson, \pmkh, W. C. Everett, G. L. Heard, D. W. Setser, and B. E. Holmes, "Unimolecular Rate Constants for HX or DX Elimination (X = F, Cl) from Chemically Activated CF 3CH 2CH 2Cl, C 2H 5CH 2Cl, and C 2D 5CH 2Cl:  Threshold Energies for HF and HCl Elimination," J. Phys. Chem. A, vol. 109, no. 20, pp. 4540-4551, May 2005.\pmid{16833790}
\item A. E. Cho, J. A. Wendel, N. Vaidehi, \pmkh, W. B. Floriano, P. K. Maiti, and W. A. Goddard, "The MPSim-Dock hierarchical docking algorithm: Application to the eight trypsin inhibitor cocrystals," J Comput Chem, vol. 26, no. 1, pp. 48-71, 2004.\pmid{15529328}
\item \pmkh, I. Muegge, and M. Rauch, "A molecular docking study of estrogenically active compounds with 1, 2-diarylethane and 1, 2-diarylethene pharmacophores," Bioorganic\& medicinal, 2004.\pmid{15556769}
\item \pmkh, N. Vaidehi, W. B. Floriano, and W. Goddard III, "Fidelity of phenylalanyl-tRNA synthetase in binding the natural amino acids," J Phys Chem B, vol. 107, no. 41, pp. 11549-11557, 2003. % Not in Pubmed

\end{etaremune}
