My research is dedicated toward understanding molecular mechanisms of biochemical signaling pathways through computational modeling. 
%My lab thus studies the interplay between molecular-scale events, such as protein-ligand (or drug) binding, and cellular-scale signaling pathways arising from interactions between proteins, that shape human health. 
These signaling pathways integrate molecular events with biological function and are often optimized to maximize speed, energy efficiency or robustness, through controlling the location, binding kinetics, and molecular composition of participating enzymes and substrates. 
My lab specifically targets \catwo\ signaling in heart cells, which began with successful collaborative studies and grant funding during my postdoctoral studies at the University of California San Diego (UCSD).
Our most recent preliminary work on calcium-regulation in two mice models, for which sarcolemmal (SL) currents are up-regulated, led us to discover the role of increased sarcoplasmic reticulum (SR) calcium load in amplifying cytosolic calcium transients.
We are currently investigating additional cellular mechanisms, by which the cardiomyocyte compensates for increased SL entry of calcium, as well as how to mitigate calcium dysregulation through targeting specific calcium-handling proteins.  
%Having been co-mentored by Andrew McCulloch (UCSD), I am well-trained in working with experimental physiologists, in addition to my strong computational training with Andy McCammon (UCSD) and Bill Goddard (Caltech). 
These projects are done in collaboration with Drs. Jon Satin, Florin Despa and Sanda Despa at the University of Kentucky, who specialize in animal models of cardiac function.
Our long term goal is to leverage these studies to understand how cardiac  signaling pathways are controlled at the cellular level and perturbed in disease, which will strengthen efforts to pharmaceutically restore normal cardiac output.
Two manuscripts nearing submission evidence major contributions from my trainees toward this goal:
\lbn
\item Scott C, Kekenes-Huskey, P. Understanding the structural changes of the calcium-binding human S100A1 protein with molecular dynamics simulations, 
\item Scott C, Atalay S, Kekenes-Huskey P. Quantifying the influence of the crowded cytoplasm on ion and small biomolecule diffusion via homogenization theory
\len
